NewAnalysis

### 2024-11-05 Code/NewAnalysis.Rmd
added log normal analysis

```{r}
set.seed(1)
sim_two_effect_time(dash_and_hurdles_two_effect_gamma_log, dash_and_hurdles_one_gamma_log, 0.1)
```
Now lets see how our results change when we include disqualifications
```{r}
dash_and_hurdles_with_dq <- times |>
  filter(Type == "F" | Type == "S") |>
  filter(Gender == "M") |>
  filter(RxnTime != 0) |>
  filter(Event == "100 Dash" | Event == "110 Hurdles") |>
  mutate(RxnTime = ifelse(RxnTime < 0, 0.000001, RxnTime))
```

@@

```{r}
set.seed(1)
sim_two_effect_time(dash_and_hurdles_with_dq_two_effect_gamma_log, dash_and_hurdles_with_dq_one_gamma_log, 0.1)
```
## Lets repeat the previous section but exclude 2022 from our results
```{r}
dash_and_hurdles_no2022 <- times |>
  filter(Type == "F" | Type == "S") |>
  filter(Gender == "M") |>
  filter(Time != "DNS" & Time != "DQ" & Time != "D") |>
  filter(RxnTime != 0) |>
  filter(Event == "100 Dash" | Event == "110 Hurdles") |>
  filter(Venue != 2022)
```

@@

```{r}
sim_two_effect_time(dash_and_hurdles_no2022_with_dq_two_effect_gamma_log, dash_and_hurdles_no2022_with_dq_one_gamma_log, 0.1)
```

>>>>

```{r}
set.seed(1)
sim_two_effect_time(dash_and_hurdles_two_effect_gamma_log, dash_and_hurdles_one_gamma_log, 0.1)
```
Now lets see how our results change when we include disqualifications
```{r}
dash_and_hurdles_with_dq <- times |>
  filter(Type == "F" | Type == "S") |>
  filter(Gender == "M") |>
  filter(RxnTime != 0) |>
  filter(Event == "100 Dash" | Event == "110 Hurdles") |>
  filter(RxnTime > 0)
  #mutate(RxnTime = ifelse(RxnTime < 0, 0.000001, RxnTime))
```

@@

```{r}
set.seed(1)
sim_two_effect_time(dash_and_hurdles_with_dq_two_effect_gamma_log, dash_and_hurdles_with_dq_one_gamma_log, 0.1)
```
## Comparison of model stats with and without dq
These are model stats for model without any disqualifications
```{r}
summary(dash_and_hurdles_two_effect_gamma_log)
```

These are model stats for model with positive disqualifications
```{r}
summary(dash_and_hurdles_with_dq_two_effect_gamma_log)
```

## Lets repeat the previous section but exclude 2022 from our results
```{r}
dash_and_hurdles_no2022 <- times |>
  filter(Type == "F" | Type == "S") |>
  filter(Gender == "M") |>
  filter(Time != "DNS" & Time != "DQ" & Time != "D") |>
  filter(RxnTime != 0) |>
  filter(Event == "100 Dash" | Event == "110 Hurdles") |>
  filter(Venue != 2022)
```

@@

```{r}
sim_two_effect_time(dash_and_hurdles_no2022_with_dq_two_effect_gamma_log, dash_and_hurdles_no2022_with_dq_one_gamma_log, 0.1)
```
## Log normal Model?
```{r}
library(tidyverse)
times <- read.csv("../Data/GLMMData.csv")
colnames(times) <- c("Venue", "Type", "Time", "RxnTime", "Gender", "Heat", "Event")
```
The data we use
```{r}
dash_and_hurdles_with_dq <- times |>
  filter(Type == "F" | Type == "S") |>
  filter(Gender == "M") |>
  filter(RxnTime != 0) |>
  filter(Event == "100 Dash" | Event == "110 Hurdles") |>
  filter(RxnTime > 0)
```

Log normal model
```{r}
library(lme4)
log_normal_model <- lmer(log(RxnTime) ~ (1 | Venue) + (1 | Heat), 
                                   data = dash_and_hurdles_with_dq)
log_normal_model
```

Current best fit model (Included DQs because that is what I believe we will
use as final model.)
```{r}
dash_and_hurdles_with_dq_two_effect_gamma_log <- glmer(RxnTime ~ (1 | Venue) +
                                                   (1 | Heat), 
                                   data = dash_and_hurdles_with_dq,
                                   family = Gamma(link = "log"))
```

Here is the qq plot for both. It looks very similar in my opinion with only some
small differences.  I think it is reasonable to keep the gamma model.  Is it not
possible to compare the AIC's? When I try to find the AIC for log normal model
I am unable to.
```{r}
library(car)
resids_log_normal <- residuals(log_normal_model)
resids_gamma <- residuals(dash_and_hurdles_with_dq_two_effect_gamma_log)
qqPlot(resids_log_normal)
qqPlot(resids_gamma)
```
